### 2021-12-06 documentos/intro.tex
dandole

Generalization of \textit{completely decoherence Pauli channels}, such as completely dephasing,
\begin{equation}
\rho \mapsto \rho_{00}\projj{0}+\rho_{11}\projj{1},
\end{equation}
and \textit{completely depolarizing},
\begin{equation}
\rho \mapsto \frac{\one}{2} \tr \rho,
\end{equation}
These channels correspond in collapsing the Bloch sphere into a line and a point, respectively. [...] Other families of channels inspired in leaving 
% }}}

>>>>

Nathanson, Ruskai~\cite{nathanson2007pauli} based on MUBs... Based on mutually unbiased measurements~\cite{Siudzinska2020}
Generalization of \textit{completely decoherence Pauli channels}, such as completely dephasing,
\begin{equation}
\rho \mapsto \rho_{00}\projj{0}+\rho_{11}\projj{1},
\end{equation}
and \textit{completely depolarizing},
\begin{equation}
\rho \mapsto \frac{\one}{2} \tr \rho,
\end{equation}
These channels correspond in collapsing the Bloch sphere into a line and a point, respectively. [...] Other families of channels inspired in leaving 
% }}}
